---
title: "Racialized Economic Concentration and Storm-Related Injuries and Deaths in the United States, 2005–2022"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center"
)
```

# Overview

This document reproduces the main and supplementary analyses for:

**"Racialized Economic Concentration and Storm-Related Injuries and Deaths in the United States, 2005–2022"**

It:
1. loads NOAA Storm Events data,
2. links storm events to county-level ICE values,
3. merges ACS population and county covariates,
4. fits primary, sensitivity, spline, and categorical models,
5. exports tables and figures.

# Reproducibility notes

- Do **not** store Census API keys directly in this file or in a public repository.
- Store raw input files in `data/raw/` and derived files in `data/derived/`.
- Outputs are written to `output/tables/` and `output/figures/`.

# Load packages

```{r packages}
required_pkgs <- c(
  "dplyr", "readr", "stringr", "purrr", "tidyr", "here",
  "glmmTMB", "broom.mixed", "modelsummary", "lmtest",
  "tidycensus", "splines", "ggeffects", "ggplot2",
  "flextable", "officer", "tigris", "sf", "viridis"
)

missing_pkgs <- required_pkgs[!vapply(required_pkgs, requireNamespace, logical(1), quietly = TRUE)]
if (length(missing_pkgs) > 0) {
  install.packages(missing_pkgs)
}

invisible(lapply(required_pkgs, library, character.only = TRUE))

options(tigris_use_cache = TRUE)
set.seed(1205)
```

# Paths and directories

```{r paths}
dir.create(here::here("data", "derived"), recursive = TRUE, showWarnings = FALSE)
dir.create(here::here("output", "tables"), recursive = TRUE, showWarnings = FALSE)
dir.create(here::here("output", "figures"), recursive = TRUE, showWarnings = FALSE)

storm_dir <- here::here("data", "raw", "stormevents")
ice_path  <- here::here("data", "raw", "racism-county-income-inequity.csv")
```

# Census API key

```{r census-key}
# Recommended: save your API key once in ~/.Renviron as:
# CENSUS_API_KEY=your_key_here

census_key <- Sys.getenv("CENSUS_API_KEY")
census_key <- Sys.getenv("badf0eedd1bb7d8401e956db4175714e4f129980") # Author's personal api key Will be removed after peer-review process.
if (nzchar(census_key)) {
  tidycensus::census_api_key(census_key, install = FALSE, overwrite = TRUE)
} else {
  warning("No Census API key found in environment variable CENSUS_API_KEY. ACS retrieval will fail unless the key is already installed.")
}
```

# Helper functions

```{r helpers}
make_merge_window <- function(year) {
  dplyr::case_when(
    year %in% c(2005, 2006) ~ "2005-2009",
    year == 2007 ~ "2006-2010",
    year == 2008 ~ "2007-2011",
    year == 2009 ~ "2008-2012",
    year == 2010 ~ "2009-2013",
    year == 2011 ~ "2010-2014",
    year == 2012 ~ "2011-2015",
    year == 2013 ~ "2012-2016",
    year == 2014 ~ "2013-2017",
    year == 2015 ~ "2014-2018",
    year == 2016 ~ "2015-2019",
    year == 2017 ~ "2016-2020",
    year == 2018 ~ "2017-2021",
    year %in% c(2019, 2020, 2021, 2022) ~ "2018-2022",
    TRUE ~ NA_character_
  )
}

fit_zinb <- function(formula, data) {
  glmmTMB(
    formula = formula,
    ziformula = ~ 1,
    family = nbinom2,
    data = data
  )
}

extract_quintile_irrs <- function(model, outcome_label) {
  broom.mixed::tidy(model, effects = "fixed", component = "cond", conf.int = TRUE) %>%
    dplyr::filter(grepl("^ice_quintile_f", term)) %>%
    dplyr::mutate(
      outcome = outcome_label,
      quintile = sub("^ice_quintile_f", "", term),
      IRR = exp(estimate),
      IRR_low = exp(conf.low),
      IRR_high = exp(conf.high),
      IRR_CI = sprintf("%.2f [%.2f, %.2f]", IRR, IRR_low, IRR_high)
    ) %>%
    dplyr::select(outcome, quintile, IRR, IRR_low, IRR_high, IRR_CI, p.value)
}

save_docx_table <- function(ft, title, path, style = "heading 1") {
  doc <- officer::read_docx()
  doc <- officer::body_add_par(doc, title, style = style)
  doc <- flextable::body_add_flextable(doc, ft)
  print(doc, target = path)
}
```

# 1. Load and combine Storm Events data

```{r storm-load}
storm_files <- list.files(
  path = storm_dir,
  pattern = "^StormEvents_details-ftp_v1\\.0_d\\d{4}_c20250520\\.csv$",
  full.names = TRUE
)

stopifnot(length(storm_files) > 0)

all_data <- purrr::map_dfr(
  storm_files,
  ~ readr::read_csv(.x, col_types = readr::cols(.default = readr::col_character()))
)

all_data <- all_data %>%
  dplyr::mutate(
    YEAR = as.integer(YEAR),
    STATE_FIPS = as.integer(STATE_FIPS),
    CZ_FIPS = as.integer(CZ_FIPS),
    EPISODE_ID = as.integer(EPISODE_ID),
    INJURIES_DIRECT = as.numeric(INJURIES_DIRECT),
    DEATHS_DIRECT = as.numeric(DEATHS_DIRECT),
    INJURIES_INDIRECT = as.numeric(INJURIES_INDIRECT),
    DEATHS_INDIRECT = as.numeric(DEATHS_INDIRECT)
  )
```

# 2. Filter years and storm event types

```{r storm-filter}
storm_event_types <- c(
  "Hurricane (Typhoon)",
  "Tropical Storm",
  "Storm Surge/Tide",
  "Coastal Flood",
  "Flash Flood",
  "High Wind",
  "Tornado"
)

data <- all_data %>%
  dplyr::filter(YEAR >= 2005, YEAR <= 2022, EVENT_TYPE %in% storm_event_types) %>%
  dplyr::mutate(
    county_fips = sprintf("%02d%03d", STATE_FIPS, CZ_FIPS),
    year = as.integer(YEAR),
    merge_window = make_merge_window(year)
  ) %>%
  dplyr::filter(!is.na(merge_window), !is.na(county_fips))
```

# 3. Load ICE data

```{r ice-load}
ice <- readr::read_csv(ice_path, show_col_types = FALSE) %>%
  dplyr::mutate(
    statefips = as.integer(statefips),
    countyfips = as.integer(countyfips),
    county_fips = sprintf("%02d%03d", statefips, countyfips),
    merge_window = year
  )

stopifnot(all(c("county_fips", "merge_window", "ice_wanh_ba") %in% names(ice)))
```

# 4. Merge storm data and ICE

```{r merge-ice}
merged_df <- data %>%
  dplyr::left_join(ice, by = c("county_fips", "merge_window"))
```

# 5. Retrieve ACS population

```{r acs-pop}
acs_windows <- c(
  "2005-2009", "2006-2010", "2007-2011", "2008-2012", "2009-2013",
  "2010-2014", "2011-2015", "2012-2016", "2013-2017", "2014-2018",
  "2015-2019", "2016-2020", "2017-2021", "2018-2022"
)
acs_end_years <- as.integer(substr(acs_windows, 6, 9))

pop_data <- purrr::map2_dfr(acs_windows, acs_end_years, ~{
  tidycensus::get_acs(
    geography = "county",
    variables = "B01003_001",
    year = .y,
    survey = "acs5",
    output = "wide"
  ) %>%
    dplyr::mutate(merge_window = .x)
}) %>%
  dplyr::transmute(
    county_fips = GEOID,
    merge_window,
    county_population = B01003_001E
  )

merged_df <- merged_df %>%
  dplyr::left_join(pop_data, by = c("county_fips", "merge_window"))
```

# 6. Retrieve ACS covariates

```{r acs-covariates}
acs_vars <- c(
  tot_pop_race = "B03002_001",
  nh_black     = "B03002_004",
  med_hh_inc   = "B19013_001",
  tot_pop_age  = "B01001_001",
  m65_66       = "B01001_020",
  m67_69       = "B01001_021",
  m70_74       = "B01001_022",
  m75_79       = "B01001_023",
  m80_84       = "B01001_024",
  m85up        = "B01001_025",
  f65_66       = "B01001_044",
  f67_69       = "B01001_045",
  f70_74       = "B01001_046",
  f75_79       = "B01001_047",
  f80_84       = "B01001_048",
  f85up        = "B01001_049"
)

acs_covars <- purrr::map2_dfr(acs_windows, acs_end_years, ~{
  tidycensus::get_acs(
    geography = "county",
    variables = acs_vars,
    year = .y,
    survey = "acs5",
    output = "wide"
  ) %>%
    dplyr::mutate(merge_window = .x)
}) %>%
  dplyr::mutate(
    county_fips = GEOID,
    pct_black = 100 * (nh_blackE / tot_pop_raceE),
    median_hh_income = med_hh_incE,
    pop_65plus = m65_66E + m67_69E + m70_74E + m75_79E + m80_84E + m85upE +
      f65_66E + f67_69E + f70_74E + f75_79E + f80_84E + f85upE,
    pct_age65 = 100 * (pop_65plus / tot_pop_ageE)
  ) %>%
  dplyr::select(county_fips, merge_window, pct_black, median_hh_income, pct_age65)

merged_df <- merged_df %>%
  dplyr::left_join(acs_covars, by = c("county_fips", "merge_window")) %>%
  dplyr::mutate(
    pct_black_z = as.numeric(scale(pct_black)),
    median_hh_income_z = as.numeric(scale(median_hh_income)),
    pct_age65_z = as.numeric(scale(pct_age65))
  )
```

# 7. Construct analytic variables

```{r analytic-vars}
merged_df <- merged_df %>%
  dplyr::filter(!is.na(ice_wanh_ba), !is.na(county_population), county_population > 0) %>%
  dplyr::mutate(
    ice_quintile = dplyr::ntile(ice_wanh_ba, 5),
    ice_quintile_f = factor(
      ice_quintile,
      levels = c(1, 2, 3, 4, 5),
      labels = c("Q1", "Q2", "Q3", "Q4", "Q5")
    ),
    log_pop = log(county_population)
  )

readr::write_csv(merged_df, here::here("data", "derived", "analytic_dataset.csv"))
```

# 8. Descriptive table by ICE quintile
 
```{r table1}
summary_table <- merged_df %>%
  dplyr::group_by(ice_quintile) %>%
  dplyr::summarise(
    Counties = dplyr::n_distinct(county_fips),
    `Storm Events` = dplyr::n_distinct(EPISODE_ID),
    `Direct Injuries (per 100,000 people)` = mean((INJURIES_DIRECT / county_population) * 1e5, na.rm = TRUE),
    `Direct Deaths (per 100,000 people)` = mean((DEATHS_DIRECT / county_population) * 1e5, na.rm = TRUE),
    `Indirect Injuries (per 100,000 people)` = mean((INJURIES_INDIRECT / county_population) * 1e5, na.rm = TRUE),
    `Indirect Deaths (per 100,000 people)` = mean((DEATHS_INDIRECT / county_population) * 1e5, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  dplyr::mutate(dplyr::across(where(is.numeric), ~round(.x, 2)))

ft_summary <- flextable::flextable(summary_table) %>%
  flextable::autofit() %>%
  flextable::set_table_properties(layout = "autofit", width = 0.95)

save_docx_table(
  ft = ft_summary,
  title = "Storm-Related Health Outcomes by ICE Quintile, 2005–2022",
  path = here::here("output", "tables", "ICE_Descriptive_Stats_Per100k.docx")
)
```

# 9. Primary and sensitivity models

```{r primary-models}
model_di_linear <- fit_zinb(INJURIES_DIRECT ~ ice_quintile + offset(log(county_population)) + (1 | county_fips), merged_df)
model_dd_linear <- fit_zinb(DEATHS_DIRECT ~ ice_quintile + offset(log(county_population)) + (1 | county_fips), merged_df)
model_ii_linear <- fit_zinb(INJURIES_INDIRECT ~ ice_quintile + offset(log(county_population)) + (1 | county_fips), merged_df)
model_id_linear <- fit_zinb(DEATHS_INDIRECT ~ ice_quintile + offset(log(county_population)) + (1 | county_fips), merged_df)

model_di_linear_adj <- fit_zinb(INJURIES_DIRECT ~ ice_quintile + pct_black_z + median_hh_income_z + pct_age65_z + offset(log(county_population)) + (1 | county_fips), merged_df)
model_dd_linear_adj <- fit_zinb(DEATHS_DIRECT ~ ice_quintile + pct_black_z + median_hh_income_z + pct_age65_z + offset(log(county_population)) + (1 | county_fips), merged_df)
model_ii_linear_adj <- fit_zinb(INJURIES_INDIRECT ~ ice_quintile + pct_black_z + median_hh_income_z + pct_age65_z + offset(log(county_population)) + (1 | county_fips), merged_df)
model_id_linear_adj <- fit_zinb(DEATHS_INDIRECT ~ ice_quintile + pct_black_z + median_hh_income_z + pct_age65_z + offset(log(county_population)) + (1 | county_fips), merged_df)
```

```{r primary-models-table}
reg_table_adj <- modelsummary::modelsummary(
  list(
    "Direct injuries (base)" = model_di_linear,
    "Direct injuries (+ACS)" = model_di_linear_adj,
    "Direct deaths (base)" = model_dd_linear,
    "Direct deaths (+ACS)" = model_dd_linear_adj,
    "Indirect injuries (base)" = model_ii_linear,
    "Indirect injuries (+ACS)" = model_ii_linear_adj,
    "Indirect deaths (base)" = model_id_linear,
    "Indirect deaths (+ACS)" = model_id_linear_adj
  ),
  component = "cond",
  exponentiate = TRUE,
  statistic = "conf.int",
  coef_map = c(
    "ice_quintile" = "ICE quintile (per 1-quintile)",
    "pct_black_z" = "% non-Hispanic Black (z)",
    "median_hh_income_z" = "Median HH income (z)",
    "pct_age65_z" = "% age ≥65 (z)"
  ),
  stars = TRUE,
  fmt = 2,
  output = "flextable"
)

save_docx_table(
  ft = reg_table_adj,
  title = "Sensitivity models adjusting for county sociodemographics (ACS)",
  path = here::here("output", "tables", "ICE_Models_ACS_Adjusted.docx")
)
```

# 10. Spline models

```{r spline-models}
model_di_spline <- fit_zinb(INJURIES_DIRECT ~ splines::ns(ice_wanh_ba, df = 3) + offset(log_pop) + (1 | county_fips), merged_df)
model_dd_spline <- fit_zinb(DEATHS_DIRECT ~ splines::ns(ice_wanh_ba, df = 3) + offset(log_pop) + (1 | county_fips), merged_df)
model_ii_spline <- fit_zinb(INJURIES_INDIRECT ~ splines::ns(ice_wanh_ba, df = 3) + offset(log_pop) + (1 | county_fips), merged_df)
model_id_spline <- fit_zinb(DEATHS_INDIRECT ~ splines::ns(ice_wanh_ba, df = 3) + offset(log_pop) + (1 | county_fips), merged_df)
```

```{r spline-curves}
get_irr_curve <- function(model, data, ice_var = "ice_wanh_ba", q = c(0.01, 0.99), outcome_label = "Outcome", offset_var = "log_pop", offset_value = 0) {
  pred <- ggeffects::ggpredict(
    model,
    terms = paste0(ice_var, " [all]"),
    type = "count",
    condition = setNames(offset_value, offset_var)
  ) %>%
    as.data.frame()

  if (!"x" %in% names(pred)) {
    if (ice_var %in% names(pred)) pred$x <- pred[[ice_var]] else stop("Could not find predictor column in ggpredict output.")
  }

  xr <- as.numeric(stats::quantile(data[[ice_var]], probs = q, na.rm = TRUE))
  pred <- pred %>% dplyr::filter(x >= xr[1], x <= xr[2])

  if (any(pred$x == 0)) {
    ref <- pred$predicted[pred$x == 0][1]
  } else {
    ref_row <- ggeffects::ggpredict(
      model,
      terms = paste0(ice_var, " [0]"),
      type = "count",
      condition = setNames(offset_value, offset_var)
    ) %>% as.data.frame()
    ref <- ref_row$predicted[1]
  }

  pred %>%
    dplyr::mutate(
      IRR = predicted / ref,
      IRR_low = conf.low / ref,
      IRR_high = conf.high / ref,
      outcome = outcome_label
    )
}

pred_all <- dplyr::bind_rows(
  get_irr_curve(model_di_spline, merged_df, outcome_label = "Direct injuries"),
  get_irr_curve(model_dd_spline, merged_df, outcome_label = "Direct deaths"),
  get_irr_curve(model_ii_spline, merged_df, outcome_label = "Indirect injuries"),
  get_irr_curve(model_id_spline, merged_df, outcome_label = "Indirect deaths")
)

panel_plot <- ggplot2::ggplot(pred_all, ggplot2::aes(x = x, y = IRR)) +
  ggplot2::geom_ribbon(ggplot2::aes(ymin = IRR_low, ymax = IRR_high), alpha = 0.2) +
  ggplot2::geom_line(linewidth = 1.1) +
  ggplot2::geom_hline(yintercept = 1, linetype = "dashed", alpha = 0.5) +
  ggplot2::facet_wrap(~ outcome, nrow = 2, scales = "free_y") +
  ggplot2::labs(
    x = "ICE (racialized economic concentration)",
    y = "Incidence rate ratio (IRR), referenced to ICE = 0"
  ) +
  ggplot2::theme_minimal(base_size = 13)

panel_plot

ggplot2::ggsave(
  filename = here::here("output", "figures", "panel_plot_spline_offset.tiff"),
  plot = panel_plot,
  width = 10,
  height = 7,
  dpi = 600,
  units = "in",
  compression = "lzw"
)
```

# 11. Model diagnostics

```{r diagnostics}
AIC_comparison <- tibble::tibble(
  Outcome = c("Direct injuries", "Direct deaths", "Indirect injuries", "Indirect deaths"),
  Linear_AIC = c(AIC(model_di_linear), AIC(model_dd_linear), AIC(model_ii_linear), AIC(model_id_linear)),
  Spline_AIC = c(AIC(model_di_spline), AIC(model_dd_spline), AIC(model_ii_spline), AIC(model_id_spline))
) %>%
  dplyr::mutate(Delta_AIC = Linear_AIC - Spline_AIC)

AIC_comparison

lr_di <- lmtest::lrtest(model_di_linear, model_di_spline)
lr_dd <- lmtest::lrtest(model_dd_linear, model_dd_spline)
lr_ii <- lmtest::lrtest(model_ii_linear, model_ii_spline)
lr_id <- lmtest::lrtest(model_id_linear, model_id_spline)

lr_di
lr_dd
lr_ii
lr_id
```

# 12. Categorical ICE sensitivity analysis

```{r categorical-models}
m_di_cat <- fit_zinb(INJURIES_DIRECT ~ ice_quintile_f + offset(log(county_population)) + (1 | county_fips), merged_df)
m_dd_cat <- fit_zinb(DEATHS_DIRECT ~ ice_quintile_f + offset(log(county_population)) + (1 | county_fips), merged_df)
m_ii_cat <- fit_zinb(INJURIES_INDIRECT ~ ice_quintile_f + offset(log(county_population)) + (1 | county_fips), merged_df)
m_id_cat <- fit_zinb(DEATHS_INDIRECT ~ ice_quintile_f + offset(log(county_population)) + (1 | county_fips), merged_df)

cat_irrs <- dplyr::bind_rows(
  extract_quintile_irrs(m_di_cat, "Direct injuries"),
  extract_quintile_irrs(m_dd_cat, "Direct deaths"),
  extract_quintile_irrs(m_ii_cat, "Indirect injuries"),
  extract_quintile_irrs(m_id_cat, "Indirect deaths")
)

cat_irrs
```

```{r categorical-table}
tab_wide <- cat_irrs %>%
  dplyr::select(outcome, quintile, IRR_CI) %>%
  tidyr::pivot_wider(names_from = outcome, values_from = IRR_CI) %>%
  dplyr::arrange(factor(quintile, levels = c("Q2", "Q3", "Q4", "Q5")))

ft_cat <- flextable::flextable(tab_wide) %>%
  flextable::set_header_labels(
    quintile = "ICE quintile (ref = Q1)",
    `Direct injuries` = "Direct injuries IRR [95% CI]",
    `Direct deaths` = "Direct deaths IRR [95% CI]",
    `Indirect injuries` = "Indirect injuries IRR [95% CI]",
    `Indirect deaths` = "Indirect deaths IRR [95% CI]"
  ) %>%
  flextable::autofit()

save_docx_table(
  ft = ft_cat,
  title = "Supplementary Table 2. Multilevel zero-inflated negative binomial regression estimates using ICE quintiles as a categorical exposure (reference = Q1, most disadvantaged)",
  path = here::here("output", "tables", "supp_table_quintiles.docx"),
  style = "heading 2"
)
```

```{r categorical-figure}
cat_irrs_plot <- cat_irrs %>%
  dplyr::mutate(
    outcome = factor(outcome, levels = c("Direct injuries", "Direct deaths", "Indirect injuries", "Indirect deaths")),
    quintile = factor(quintile, levels = c("Q2", "Q3", "Q4", "Q5"))
  )

forest_plot <- ggplot2::ggplot(cat_irrs_plot, ggplot2::aes(x = quintile, y = IRR, ymin = IRR_low, ymax = IRR_high)) +
  ggplot2::geom_pointrange() +
  ggplot2::geom_hline(yintercept = 1, linetype = "dashed", alpha = 0.6) +
  ggplot2::facet_wrap(~ outcome, scales = "free_y", nrow = 2) +
  ggplot2::labs(
    x = "ICE quintile (reference = Q1, most disadvantaged)",
    y = "Incidence rate ratio (IRR)"
  ) +
  ggplot2::theme_minimal(base_size = 13)

forest_plot

ggplot2::ggsave(
  filename = here::here("output", "figures", "supp_forestplot_quintiles.tiff"),
  plot = forest_plot,
  width = 10,
  height = 7,
  dpi = 600,
  units = "in",
  compression = "lzw"
)
```

# 13. ICE distribution figure

```{r ice-hist}
hist_plot <- ggplot2::ggplot(merged_df, ggplot2::aes(x = ice_wanh_ba)) +
  ggplot2::geom_histogram(binwidth = 0.05, color = "black", fill = "gray60", boundary = 0) +
  ggplot2::labs(
    x = "ICE score (racialized economic concentration)",
    y = "Number of county-event observations"
  ) +
  ggplot2::theme_classic(base_size = 14) +
  ggplot2::theme(
    axis.title = ggplot2::element_text(face = "bold"),
    axis.text = ggplot2::element_text(color = "black")
  )

hist_plot

ggplot2::ggsave(
  filename = here::here("output", "figures", "ice_score_histogram.jpg"),
  plot = hist_plot,
  dpi = 600,
  width = 8,
  height = 5,
  units = "in"
)
```

# 14. County maps

```{r county-maps}
# Most frequent ICE quintile per county across the study period
ice_mode <- merged_df %>%
  dplyr::group_by(county_fips) %>%
  dplyr::summarise(
    ice_quintile_mode = as.integer(names(which.max(table(ice_quintile)))),
    total_events = dplyr::n(),
    .groups = "drop"
  )

us_counties <- tigris::counties(cb = TRUE, resolution = "5m", year = 2020) %>%
  sf::st_transform(crs = 4326) %>%
  dplyr::mutate(county_fips = GEOID)

exclude_states <- c("02", "15", "60", "66", "69", "72", "78")

map_data_conus <- us_counties %>%
  dplyr::left_join(ice_mode, by = "county_fips") %>%
  dplyr::filter(!(STATEFP %in% exclude_states))

ice_map <- ggplot2::ggplot(map_data_conus) +
  ggplot2::geom_sf(ggplot2::aes(fill = factor(ice_quintile_mode)), color = NA) +
  viridis::scale_fill_viridis(discrete = TRUE, name = "ICE Quintile\n(mode, 2005–2022)", na.value = "lightgray") +
  ggplot2::labs(title = "County-level ICE quintiles") +
  ggplot2::theme_void() +
  ggplot2::theme(
    plot.title = ggplot2::element_text(hjust = 0.5, face = "bold", size = 16),
    legend.title = ggplot2::element_text(size = 12),
    legend.text = ggplot2::element_text(size = 10)
  )

events_map <- ggplot2::ggplot(map_data_conus) +
  ggplot2::geom_sf(ggplot2::aes(fill = total_events), color = NA) +
  viridis::scale_fill_viridis(
    option = "magma",
    direction = -1,
    trans = "log10",
    name = "Storm events\n(2005–2022)",
    na.value = "lightgray"
  ) +
  ggplot2::labs(title = "Total storm-related events per county (2005–2022)") +
  ggplot2::theme_void() +
  ggplot2::theme(
    plot.title = ggplot2::element_text(hjust = 0.5, face = "bold", size = 16),
    legend.title = ggplot2::element_text(size = 12),
    legend.text = ggplot2::element_text(size = 10)
  )

ice_map
events_map

ggplot2::ggsave(here::here("output", "figures", "ICE_quintile_mode_map.png"), ice_map, width = 10, height = 6, dpi = 300)
ggplot2::ggsave(here::here("output", "figures", "storm_event_map_conus.png"), events_map, width = 10, height = 6, dpi = 300)
```
